Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-01-19 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
comments!

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores. 
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore two variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center. Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  of which has separate transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. 
  %BJC7: added  
  However, qualitative differences between MD and simulated MSDDM trajectories
  may limit its usefulness. 
  Finally, we demonstrate how one can use our models to estimate flux of a solute
  across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
  This work helps to connect microscopic chemically-dependent solute 
  motions and macroscopic membrane performance.

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to conventional membrane separation techniques
  by being selective based not only on solute size and charge, but on solute chemical 
  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two general morphologies of LLC membranes are being actively developed. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations, however aligning the microscopic hexagonal mesophases on a large 
  scale has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.~\cite{hatakeyama_nanoporous_2010}

@@

  In our previous work,~\cite{coscia_chemically_2019} we used molecular dynamics (MD) 
  simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
  phase LLC membrane.
  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
  %BJC6: I said above how the QI phase is easier to synthesize, so I felt it necessary to 
  % quickly justify why we studied the HII phase. Reworded to make that clearer. I'm also open to
  % eliminating the sentence.
  %MRS6: It was also becasue they thought it was more likely to be interesting initially.  I'm in favor of 
  % cutting for simplicity. 
  We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
  the Q\textsubscript{I} phase.  
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

@@

%  By reducing our MD simulations to observations of several key properties that 
%  have the greatest influence on solute dynamics, we can construct many realizations
%  of single solute trajectories useful for making long timescale predictions with 
%  computational ease and lower uncertainties. Fortunately, there is an abundance of 
%  information encoded in the complex solute trajectories. Into a model, we can 
%  incorporate fluctuations and time-dependent correlations in solute position as well
%  as the length of time solutes are trapped. We can add further detail by integrating
%  our time series analysis with our knowledge of the primary trapping mechanisms as
%  well as the solute's changing chemical environment within the heterogeneous membrane.

@@

  %BJC4: making goals more explicit
  We determine the degree of success of our modeling approaches in two ways. First,
  if we can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  dynamics in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of overfitting.

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on a given research study's goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.5\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  \end{figure}

@@

  We primarily use the MSD as a tool for calculating the average properties of 
  solute trajectories. We only compare MSDs calculated from MD simulations to 
  those generated from our models. We do not use them to calculate diffusion 
  constants or to relate our simulations to experimental measurements. Therefore
  it is only important that we use a consistent definition for calculating the MSD.
%  This approach is valid if we adhere to a consistent definition for MSD 
%  calculations.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. The ensemble MSD of only 24 solute trajectories would
  have much higher uncertainties.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  %We cannot observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated paramters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  Since we also want to account for the possibility that distribution of hops is 
  not Gaussian, we can model them with the more general class of L\'evy stable 
  distributions. For independent and identically distributed random variables, 
  the generalized central limit theorem assures convergence of the associated 
  probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
  The characteristic equation which describes the Fourier transform of a L\'evy stable PDF is:
  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
  \begin{equation}
    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
  \end{equation}
  where \\
  \[\omega(k, \alpha_h) = \begin{cases}
  	\tan{\frac{\pi \alpha_h}{2}} & \text{if}~\alpha_h \neq 1, 0 < \alpha_h < 2, \\
  	-\frac{2}{\pi}\ln |k| & \text{if}~\alpha_h = 1
  	 \end{cases}
  \]
  $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
  familiar case, and one of three that can be expressed in terms of elementary functions,
  is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
  centered about 0 implying that $\beta$ and $\mu$ are both 0.

@@

  Analogous to power law dwell times, the heavy tails of L\'evy stable 
  hop length distributions result in rare but arbitrarily long hops. These long
  and unrealistic hops result in over-estimated simulated MSDs. We observe that
  the distribution of hops observed in our MD simulations are well approximated 
  by L\'evy stable distributions close to the mean, but they significantly under-sample
  the tails. We chose to truncate the L\'evy stable distributions based
  on where the theoretical probability distribution function (PDF) starts to 
  deviate from the empirically measured PDF (see Section~\ref{S-section:truncation}
  of the Supporting Information).~\cite{mantegna_stochastic_1994}

@@

  We simulated models with all combinations of the types of dwell and hop length
  distributions described above, which are summarized in Table~\ref{table:anomalous_models}.
  All models include correlation between hops.

@@

  %BJC6: added this. Not sure how much detail is necessary
  %MRS7: seems fine.
  We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
  and AD model trajectories then estimated their uncertainty using statistical 
  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute trajectories,
  where $n$ is the number of independent trajectories, with replacement from the 
  ensemble of trajectories and then calculated the MSD of the subset. We reported 
  the time-averaged MSD up to a 1000 ns time lag with corresponding 1$\sigma$ confidence
  intervals. 
  %MRS6: somewhere you do talk about agreement to within 1 sigma
  %instead of 95%, so probably should check for consistance.

@@

  %BJC3: not sure how to cite fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories. However, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
  validation of the approach).
  % MRS6: suggest in the supporting information describe what measure was used to 
  % determine that the algorithm sufficiently and reasonably approxmiates.

@@

  %BJC6: could defer most of this to supporting.  
  %MRS7: yeah, supporting.  Should just be ``Verified the Markovianity of state transitions in MD as described in Section [X]. Generally, how one did verification of most things can be put in supporing, since that's not central to the argument. ''
%  We verified the Markovianity of state transitions by solutes in our MD simulations 
%  by analyzing the empirically measured transition matrix. An important condition
%  of a Markov process is the satisfaction of detailed balance:
%  \begin{equation}
%  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
%  \end{equation}
%  where $P$ is the equilibrium distribution of states. In other words, the number of
%  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
%  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
%  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
%  with time.~\cite{swope_describing_2004} We verified these properties 
%  in Section~\ref{S-section:markov_validation} of the Supporting Information.

@@

  We generated particle trajectories, parameterized with the above models, in order
  to construct a distribution of first passage times across a membrane pore of length $L$.
  For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
  realizations, released at the pore entrance ($z=0$). In the case of 
  uncorrelated hops, one can continuously draw from the hop length distribution until 
  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
  single passage time. When particle hops are correlated, as they are in all cases of
  this work, we cannot continuously construct the particle trajectories. Rather, we must
  generate trajectories of length $n$ and measure the length of the sub-trajectory 
  which traverses from $0$ to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

@@

  To derive an analytical equation describing the passage time distributions, 
  one can frame the 
  problem as a pulse of particles instantaneously released at the pore inlet ($z=0$)
  which moves at a constant velocity, $v$, and spreads out as it approaches $L$. 
  This spreading is parameterized by an effective diffusivity parameter, $D$. This 
  approach gives results equivalent to if we had released each particle individually
  and then analyzed the positions of the ensemble of trajectories as 
  a function of time. The analytical expression describing the distribution of 
  first passage times is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. A derivation
  of Equation~\ref{eqn:passage_times} is given in Section~\ref{S-section:fpt_derivation}
  of the Supporting Information. We calculated the expected value of 
  Equation~\ref{eqn:passage_times} in order to get the MFPT.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:solute_trajectories}, we plotted representative
  trajectories for each solute. They are characterized by intermittent hops between
  periods of entrapment. The near-Gaussian distribution of jump lengths and power law 
  distribution of dwell times are both characteristic of CTRWs 
  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate 
  to the CTRW. Of the different models, a process subordinated by FBM or FLM is best 
  supported by the data because the analytical correlation structures of hop lengths are
  close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional 
  motion is common in crowded viscoelastic environments where movement is highly 
  influenced by the movement of surrounding components, such as monomer tails in our 
  case.~\cite{ernst_fractional_2012}

@@

  Given stationary data, the AD model is capable of predicting solute MSDs 
  measured from MD simulations within or near statistical uncertainty.
  In Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized 
  the AD model using the first half of the stationary solute equilibrated trajectories 
  and then compared the model predictions to the MD MSD of the second of half 
  of the stationary trajectories. In most cases, the model predictions fall within
  the 1$\sigma$ confidence intervals of the MD MSD.

>>>>

  Mathematically modeling complex transport phenomena at the molecular level 
  can be a powerful tool for identifying transport mechanisms and predicting
  macroscopic properties. We use two different stochastic time series models,
  parameterized from long molecular dynamics (MD) simulation trajectories of
  a cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membrane, in order to predict solute mean squared displacements (MSDs) 
  and solute flux, and thus solute selectivity, in macroscopic length pores. 
  First, using anomalous diffusion theory, we show how solute dynamics can be
  modeled as a fractional diffusion process subordinate to a continuous time 
  random walk. From the MD simulations, we parameterize the distribution of 
  dwell times, hop lengths between dwells and correlation between hops. We 
  explore two variations of the anomalous diffusion model. The first variation
  applies a single set of parameters to the solute displacements and the second
  applies two sets of parameters based on the solute's radial distance from the
  closest pore center. Next, we generalize Markov state models, treating the
  configurational state of the system as a Markov process, each
  of which has separate transport properties. For each state and transition
  between states, we parameterize the distribution and temporal correlation 
  structure of positional fluctuations as a means of characterization and to 
  allow us to predict solute MSDs. We show that both models reasonably reproduce
  the MSDs calculated from MD simulations. 
  However, qualitative differences between MD and 
  %simulated MSDDM 
  MSDDM-generated  %MRS: abbreviation not defined first? Maybe eliminate here, just call it the Markov State dependent model
  trajectories
  may limit its usefulness. 
  Finally, we demonstrate how one can use 
  %our 
  these 
  models to estimate flux of a solute
  across a macroscopic-length pore and, based on those quantities, the membrane's selectivity towards each solute.
  This work helps to connect microscopic chemically-dependent solute 
  motions 
  %MRS8:  Added the below, since for simple diffusion, you just calculate the diffusion constant. 
  %and 
  that do not follow simple diffusive behavior with 
  macroscopic membrane performance.

@@

  Lyotropic liquid crystals (LLCs) are a class of amphiphilic molecules that can be 
  cross-linked into mechanically strong and highly selective nanoporous membranes.~\cite{gin_polymerized_2008}
  They may provide a promising alternative to conventional membrane separation techniques
  by being selective based not only on solute size and charge, but on solute chemical 
  functionality as well.~\cite{dischinger_application_2017} One can tune the functionality
  of LLC monomers in order to enhance or weaken specific solute-membrane interactions.~\cite{dischinger_effect_2017}
  Two general morphologies of LLC membranes are being actively developed. The inverted hexagonal, 
  H\textsubscript{II}, LLC phase has densely packed, uniform-sized pores on the order of 1 nm
  in size. A perfectly synthesized H\textsubscript{II} phase has an ideal geometry for high
  throughput separations. 
  %MRS8: break sentence, tweak phrasing.
  %however 
  Unfortunately, aligning the microscopic hexagonal mesophases on a large 
  scale 
  as required for high permeability
  has shown limited success.~\cite{feng_scalable_2014,feng_thin_2016} Bicontinuous cubic,
  Q\textsubscript{I}, phase LLCs share the uniform and nm-sized chemically complex pores of
  the H\textsubscript{II} phase but its geometry consists of a tortuous network of 3D 
  interconnected pores which do not require alignment.~\cite{carter_glycerol-based_2012} While 
  its pore structure may decrease a Q\textsubscript{I} membrane's permeability relative to the
  H\textsubscript{II} phase, it is considerably easier to synthesize at scale.~\cite{hatakeyama_nanoporous_2010}

@@

  In our previous work,~\cite{coscia_chemically_2019} we used molecular dynamics (MD) 
  simulations to study the transport of 20 small polar molecules in an H\textsubscript{II}
  phase LLC membrane.
  %MRS6: sentence seems out of place here? True, but does it support the thesis here?
  %BJC6: I said above how the QI phase is easier to synthesize, so I felt it necessary to 
  % quickly justify why we studied the HII phase. Reworded to make that clearer. I'm also open to
  % eliminating the sentence.
  %MRS6: It was also because they thought it was more likely to be interesting initially.  I'm in favor of 
  % cutting for simplicity. 
  We chose to study the H\textsubscript{II} phase because it is a simpler geometry to model than 
  the Q\textsubscript{I} phase
  %MRS8: added as more clarification
  and significantly more structural data is available to help ensure molecular models are consistent with experiment.
  In general, we observed subdiffusive transport behavior characterized by intermittent hops 
  separated by periods of entrapment. We identified three mechanisms responsible for the 
  solute trapping behavior: entanglement among monomer tails, hydrogen bonding with monomer
  head groups, and association with the monomer's sodium counter ions.

@@

  %MRS8: really nice flow in the introduction up through here.
%  By reducing our MD simulations to observations of several key properties that 
%  have the greatest influence on solute dynamics, we can construct many realizations
%  of single solute trajectories useful for making long timescale predictions with 
%  computational ease and lower uncertainties. Fortunately, there is an abundance of 
%  information encoded in the complex solute trajectories. Into a model, we can 
%  incorporate fluctuations and time-dependent correlations in solute position as well
%  as the length of time solutes are trapped. We can add further detail by integrating
%  our time series analysis with our knowledge of the primary trapping mechanisms as
%  well as the solute's changing chemical environment within the heterogeneous membrane.

@@

  %BJC4: making goals more explicit
  We determine the degree of success of our modeling approaches in two ways. First,
  if we can closely reproduce solute MSDs measured from MD simulations with realizations
  of our models, then it is likely that the model sufficiently captures solute 
  dynamics and can be used in a predictive capacity. Even if a model fails to 
  reproduce the MD MSDs, there is value in uncovering the cause of the deviation.
  The second measure of success is by analysis of the parameters defining each 
  model. The parameters themselves should provide clues that help explain solute 
  dynamics in a coherent way. A model that successfully reproduces MD MSDs, but 
  with nonsensical parameters has severely diminished value as it could be a 
  consequence of over-fitting.

  % BJC4: new paragraph
  The goal of this work is not to definitively determine which modeling approach
  is better but to evaluate their performance independently because they both
  have potential value dependent on a given research study's goals. The anomalous subdiffusion
  approach provides a systematic way to compare the dynamical behavior of different
  solutes based solely on the time series of their center of mass positions. The process
  of choosing the correct anomalous subdiffusion provides its own mechanistic insight
  since it requires a thorough analysis of solute time series behavior. One can simulate
  different solutes, compare the fit model parameters and relate them back to 
  differences in solute size and chemical composition. 
  %MRS8: this may be a bit of a stretch, since it's not clear it helps that much in the end, but 
  %is fine to leave in now - maybe we revisit if needed during revisions.
  The MSDDM characterizes 
  explicitly defined trapping mechanisms, providing a clear picture of solute behavior
  while in each trapped state as well as the equilibrium occupation of each trapping state.
  It is possible to use the two models in tandem, the anomalous diffusion model to
  identify mechanisms, and the MSDDM to characterize mechanisms.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=\textwidth]{NaGA3C11.pdf}
  \caption{}\label{fig:monomer_structure}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=0.5\textwidth]{membrane_profile.pdf}
  \caption{}\label{fig:membrane_profile}
  \end{subfigure}
  \caption{(a) The wedge-shaped liquid crystal monomer Na-GA3C11 will form the inverted
  hexagonal phase in the presence of water where the carboxylate head groups occupy the
  pore centers. (b) A cross-section of a periodically replicated atomistic unit cell 
  used for simulations in this study reveals the membrane's aqueous, hexagonally packed,
  straight and uniform sized pores. Water present in the tail region is omitted 
  for clarity.}\label{fig:membrane_structure}
  %MRS8: should say something about the molecular colors for (b) so it's clear what is what. 
  \end{figure}

@@

  %MRS8: some tweaks

  In this study, we primarily use the MSD as a tool for characterizing
  the average dynamic behavior solute trajectories. Rather than using
  them to calculate diffusion constants or to relate our simulations
  to experimental measurement, we compare MSDs calculated from MD
  simulations to those generated from our models in order to validate
  those models. Therefore, it is only important that we use a
  consistent definition for calculating the MSD between modeled
  trajectories and directly observed MD trajectories.

@@

  We chose to 
  %MRS8: tweaked.
  %analyze 
  use 
  just the time-averaged MSD 
  to compare MD trajectory and modeled trajectories,
  because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. The ensemble MSD of only 24 solute trajectories would
  have much higher uncertainties.

@@

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  %We cannot observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. A standard way of 
  doing this, with easily estimated parameters, is by adding an exponential 
  cut-off to the power law so the dwell time distribution is now proportional 
  to $t^{-1 - \alpha}e^{-\lambda t}$.~\cite{newman_power_2005,clauset_power-law_2009}  % Clauset uses data from other papers and gives a bunch of example where the cut-off is the most favorable model. 
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  %Since 
  Because
  we also want to account for the possibility that distribution of hops is 
  not Gaussian, we can model them with the more general class of L\'evy stable 
  distributions. For independent and identically distributed random variables, 
  the generalized central limit theorem assures convergence of the associated 
  probability distribution function (PDF) to a L\'evy stable PDF. \cite{klages_anomalous_2008}
  The characteristic equation which describes the Fourier transform of a L\'evy stable PDF is:
  %MRS6: maybe use just $\alpha$ for the general subdiffusive case, and alpha_h here.   
  \begin{equation}
    p_{\alpha_h, \beta}(k;\mu,\sigma) =\exp\left[i\mu k - \sigma^{\alpha_h}|k|^{\alpha_h}\left(1 - i\beta\frac{k}{|k|}\omega(k, \alpha_h)\right)\right]
  \end{equation}
  where \\
  \[\omega(k, \alpha_h) = \begin{cases}
  	\tan{\frac{\pi \alpha_h}{2}} & \text{if}~\alpha_h \neq 1, 0 < \alpha_h < 2, \\
  	-\frac{2}{\pi}\ln |k| & \text{if}~\alpha_h = 1
  	 \end{cases}
  \]
  $\alpha_h$ is the index of stability or L\'evy index, $\beta$ is the skewness 
  parameter, $\mu$ is the shift parameter and $\sigma$ is a scale parameter. The most
  familiar case, and one of three that can be expressed in terms of elementary functions,
  is the Gaussian PDF ($\alpha_h$ = 2, $\beta$ = 0). We assume symmetric distributions
  centered about 0 implying that $\beta$ and $\mu$ are both 0.

@@

  Analogous to power law dwell times, the heavy tails of L\'evy stable 
  hop length distributions result in rare but arbitrarily long hops. These long
  and unrealistic hops result in over-estimated simulated MSDs. 
  %MRS: could reference the figure 4 here?
  We observe that
  the distribution of hops observed in our MD simulations are well approximated 
  by L\'evy stable distributions close to the mean, but they significantly under-sample
  the tails. We chose to truncate the L\'evy stable distributions based
  on where the theoretical probability distribution function (PDF) starts to 
  deviate from the empirically measured PDF (see Section~\ref{S-section:truncation}
  of the Supporting Information).~\cite{mantegna_stochastic_1994}

@@

  We simulated models with all combinations of the types of dwell and hop length
  distributions described above, summarized in Table~\ref{table:anomalous_models}.
  All models include correlation between hops.

@@

  %BJC6: added this. Not sure how much detail is necessary
  %MRS7: seems fine.
  We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
  and AD model trajectories then estimated their uncertainty using statistical 
  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute trajectories,
  where $n$ is the number of independent trajectories, with replacement, from the 
  ensemble of trajectories and then calculated the MSD of the subset. We reported 
  the time-averaged MSD up to a 1000 ns time lag with corresponding 1$\sigma$ confidence
  intervals. 
  %MRS6: somewhere you do talk about agreement to within 1 sigma
  %instead of 95%, so probably should check for consistency

@@

  %BJC3: not sure how to cite fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories. However, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
  validation of the approach).
  % MRS6: suggest in the supporting information describe what measure was used to 
  % determine that the algorithm sufficiently and reasonably approximates.

@@

  %BJC6: could defer most of this to supporting.  
  %MRS7: yeah, supporting.  Should just be ``Verified the Markovianity of state transitions in MD as described in Section [X]. Generally, how one did verification of most things can be put in supporting, since that's not central to the argument. ''
%  We verified the Markovianity of state transitions by solutes in our MD simulations 
%  by analyzing the empirically measured transition matrix. An important condition
%  of a Markov process is the satisfaction of detailed balance:
%  \begin{equation}
%  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
%  \end{equation}
%  where $P$ is the equilibrium distribution of states. In other words, the number of
%  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
%  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
%  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
%  with time.~\cite{swope_describing_2004} We verified these properties 
%  in Section~\ref{S-section:markov_validation} of the Supporting Information.

@@

  We generated particle trajectories, parameterized with the above models, in order
  to construct a distribution of first passage times across a membrane pore of length $L$.
  For computational 
  %MRS8: computational costs? Clarify.
  reasons dependent on the model used, we simulated 1,000-10,000 trajectory
  realizations, released at the pore entrance ($z=0$). In the case of 
  uncorrelated hops, one can continuously draw from the hop length distribution until 
  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
  single passage time. When particle hops are correlated, as they are in all cases of
  this work, we cannot continuously construct the particle trajectories. Rather, we must
  generate trajectories of length $n$ and measure the length of the sub-trajectory 
  which traverses from $0$ to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

@@

  To derive an analytical equation describing the passage time distributions, 
  one can frame the 
  problem as a pulse of particles instantaneously released at the pore inlet ($z=0$)
  which moves at a constant velocity, $v$, and spreads out as it approaches $L$. 
  This spreading is parameterized by an effective diffusivity parameter, $D$. This 
  approach gives results equivalent to if we had released each particle individually
  and then analyzed the positions of the ensemble of trajectories as 
  a function of time. The analytical expression describing the distribution of 
  first passage times is:~\cite{cussler_diffusion:_2009}
  \begin{equation}
  P(t) = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation} 
  where the only free parameters for fitting are $v$ and $D$. A derivation
  of Equation~\ref{eqn:passage_times} is given in Section~\ref{S-section:fpt_derivation}
  of the Supporting Information. We calculated the expected value of 
  Equation~\ref{eqn:passage_times} in order to get the MFPT.
  %MRS8: check to make sure there is goodness-of-fit checks in the SI for fitting to the analytical model.

@@

  %MRS8: be more specific about which evidence. Made a stab below.   
  %The evidence suggests
  We find the data suggest
  that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:solute_trajectories}, we plotted representative
  trajectories for each solute. They are characterized by intermittent hops between
  periods of entrapment. The near-Gaussian distribution of jump lengths and power law 
  distribution of dwell times are both characteristic of CTRWs 
  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate 
  to the CTRW. Of the different models, a process subordinated by FBM or FLM is best 
  supported by the data because the analytical correlation structures of hop lengths are
  close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional 
  motion is common in crowded viscoelastic environments where movement is highly 
  influenced by the movement of surrounding components, such as monomer tails in our 
  case.~\cite{ernst_fractional_2012}

@@

  %MRS: again ``the AD model'' is confusing since there are multiple models based on AD.   ``The AD approach''?
  Given stationary data, the AD model is capable of predicting solute MSDs 
  measured from MD simulations within or near statistical uncertainty.
  In Figure~\ref{S-fig:train_test} of the Supporting Information, we parameterized 
  the AD model using the first half of the stationary solute equilibrated trajectories 
  and then compared the model predictions to the MD MSD of the second of half 
  of the stationary trajectories. In most cases, the model predictions fall within
  the 1$\sigma$ confidence intervals of the MD MSD.
